Hexagonal binning algorithm

### 2024-05-20 supplementary/hexagon_binning_algorithm.qmd
Add bin assign plot 1

```{r}
library(ggplot2)
library(dplyr)
library(quollr)
library(readr)
library(ggforce)

@@

```{r}
all_centroids_df <- gen_centroids(bin1 = 6, q = 0.1, r2 = r2)
```

@@

```{r}
hex_param_vis <- ggplot(data = hex_grid, aes(x = x, y = y)) + 
    geom_polygon(fill = "white", color = "#bdbdbd", aes(group = hex_poly_id)) +
    geom_point(data = all_centroids_df, aes(x = c_x, y = c_y), color = "#31a354") +
    geom_point(data = all_centroids_df |> dplyr::filter(hexID == 1), aes(x = c_x, y = c_y), color = "black") + ## starting point
    geom_rect(aes(xmin = 0, xmax = 1, ymin = 0, ymax = r2), fill = "white", color = "black", alpha = 0, linewidth = 1) +
    geom_segment(x = 0, y = -0.35, xend = 1, yend = -0.35,
                 arrow = arrow(length = unit(0.03, "npc"), ends = "both"), color = "black")+
    annotate("text", x=0.5, y=-0.45, label= "r1", color = "black") +
    geom_segment(x = -0.25, y = 0, xend = -0.25, yend = r2,
                 arrow = arrow(length = unit(0.03, "npc"), ends = "both"), color = "black")+ 
    annotate("text", x=-0.35, y=1, label= "r2", color = "black") +
    geom_segment(x = -0.1 + 0.2087578, y = -0.15, xend = -0.1 + 0.2087578*2, yend = -0.15,
                   arrow = arrow(length = unit(0.03, "npc"), ends = "both"), color = "black")+ # a1 = 0.2087578
    annotate("text", x=0.2, y=-0.25, label= "a1", color = "black") +
    geom_segment(x = -0.15, y = -0.1*r2 + 0.1807896*2, xend = -0.15, yend = -0.1*r2 + 0.1807896*3,
                     arrow = arrow(length = unit(0.03, "npc"), ends = "both"), color = "black")+ # a2 = 0.1807896
    annotate("text", x=-0.15, y=0.45, label= "a2", color = "black") +
    annotate("text", x=-0.2, y=-0.35, label= "(s1, s2)", color = "black") + ## starting point
  coord_equal()
```

```{r}
#| label: fig-hex-param
#| fig-cap: "Notations for hexagonal grid configurations."

@@

>>>>

```{r}
library(ggplot2)
library(dplyr)
library(quollr)
library(readr)
library(ggforce)
library(patchwork)

@@

```{r}
all_centroids_df <- gen_centroids(bin1 = 6, r2 = r2)
```

@@

```{r}
hex_param_vis <- ggplot(data = hex_grid, aes(x = x, y = y)) + 
    geom_polygon(fill = "white", color = "#bdbdbd", aes(group = hex_poly_id)) +
    geom_point(data = all_centroids_df, aes(x = c_x, y = c_y), color = "#31a354") +
    geom_point(data = all_centroids_df |> dplyr::filter(hexID == 1), aes(x = c_x, y = c_y), color = "black") + ## starting point
    geom_rect(aes(xmin = 0 - 0.03, xmax = 1 - 0.03, ymin = 0 - 0.05, ymax = r2 - 0.05), fill = "white", color = "black", alpha = 0, linewidth = 1) +
    geom_segment(x = 0 - 0.03, y = -0.35, xend = 1 - 0.03, yend = -0.35,
                 arrow = arrow(length = unit(0.03, "npc"), ends = "both"), color = "black")+
    annotate("text", x=0.5, y=-0.45, label= "r1", color = "black") +
    geom_segment(x = -0.25, y = 0 - 0.05, xend = -0.25, yend = r2 - 0.05,
                 arrow = arrow(length = unit(0.03, "npc"), ends = "both"), color = "black")+ 
    annotate("text", x=-0.35, y=1, label= "r2", color = "black") +
    geom_segment(x = -0.1 + 0.2087578, y = -0.15, xend = -0.1 + 0.2087578*2, yend = -0.15,
                   arrow = arrow(length = unit(0.03, "npc"), ends = "both"), color = "black")+ # a1 = 0.2087578
    annotate("text", x=0.2, y=-0.25, label= "a1", color = "black") +
    geom_segment(x = -0.15, y = -0.1*r2 + 0.1807896*2, xend = -0.15, yend = -0.1*r2 + 0.1807896*3,
                     arrow = arrow(length = unit(0.03, "npc"), ends = "both"), color = "black")+ # a2 = 0.1807896
    annotate("text", x=-0.15, y=0.45, label= "a2", color = "black") +
    annotate("text", x=-0.18, y=-0.35, label= "(s1, s2)", color = "black") + ## starting point
  coord_equal()
```

```{r}
#| label: fig-hex-param
#| fig-cap: "Notations for hexagonal grid configurations."
#| out-height: 30%
#| fig-pos: H

@@

```{r}
all_centroids_df <- gen_centroids(bin1 = 3, r2 = r2)

hex_grid <- gen_hex_coord(all_centroids_df, a1 = 0.5218947)

## Data to generate circle
circles <- data.frame(
  x = c(0.422, 0.683),
  y = c(0.740, 1.19),
  r = rep(0.301316, 2)
)

emb_df1 <- tibble(emb1 = 0.58, emb2 = 0.93) |>
  add_row(emb1 = 0.5, emb2 = 1.01)

assign_data_vis1 <- ggplot(data = hex_grid, aes(x = x, y = y)) + 
  geom_polygon(fill = "white", color = "#bdbdbd", aes(group = hex_poly_id)) +
  geom_point(data = emb_df1, aes(x = emb1, y = emb2), color = "black", size = 0.7) +
  geom_text(data = all_centroids_df, aes(x = c_x, y = c_y, label = hexID), size = 5, colour = "#bdbdbd") +
  geom_circle(data = circles, aes(x0 = x, y0 = y, r = r), fill = NA) +
  geom_segment(x = 0.58, y = 0.93, xend = 0.44, yend = 0.76, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#969696") +
  geom_segment(x = 0.5, y = 1.01, xend = 0.68, yend = 1.16, 
               arrow = arrow(length = unit(0.02, "npc")), color = "#969696")

assign_data_vis2 <- ggplot(data = hex_grid, aes(x = x, y = y)) + 
  geom_polygon(fill = "white", color = "#bdbdbd", aes(group = hex_poly_id)) +
  geom_text(data = all_centroids_df, aes(x = c_x, y = c_y, label = hexID), size = 5, colour = "#bdbdbd")
```

```{r}
#| fig-width: 9
#| fig-height: 6
assign_data_vis1 + assign_data_vis2 +
  plot_layout(ncol = 2)
```
